### 2020-04-30 manuscript.rmd
Informed consent statement.
Fix format figure legends.

#### Study Setting    
We evaluated 90 consecutive VAE that occurred across 87 unique subjects, over 3.5 years in the medical intensive care unit (MICU) of the Hospital of the University of Pennsylvania (HUP), a tertiary academic medical center. All patients who depend on mechanical ventilation at HUP were monitored for VAE, and all VAE were reported to NHSN. VAC and IVAC were captured by review of HUP NHSN reporting records. The study was approved by the University of Pennsylvania Institutional Review Board (protocol #824613).

@@

Supplemental Figure 2. Exploratory analyses of clinical variables that discriminate IVAC and VAC suggest a role for AST, ALT, number of pressors, and number of antibiotics.  
The association between the sum of AST and ALT and probability of IVAC versus VAC are shown, stratied by number of pressors and number of antibiotics. Best estimates of the associations are represented with a dark line, surrounded by bands of posterior certainty.

>>>>

#### Study Setting    
We evaluated 90 consecutive VAE that occurred across 87 unique subjects, over 3.5 years in the medical intensive care unit (MICU) of the Hospital of the University of Pennsylvania (HUP), a tertiary academic medical center. All patients who depend on mechanical ventilation at HUP were monitored for VAE, and all VAE were reported to NHSN. VAC and IVAC were captured by review of HUP NHSN reporting records. The study was approved by the University of Pennsylvania Institutional Review Board (protocol #824613) with a waiver of informed consent.

@@

#### Supplemental Figure 2. Exploratory analyses of clinical variables that discriminate IVAC and VAC suggest a role for AST, ALT, number of pressors, and number of antibiotics.   
The association between the sum of AST and ALT and probability of IVAC versus VAC are shown, stratified by number of pressors and number of antibiotics. Best estimates of the associations are represented with a dark line, surrounded by bands of posterior certainty.
